Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Screenshots for passes of Kruger method
Fixed XML listing for swapped order of approaches

To apply ray-casting to volume rendering with a high-level programmable shading
language, \cite{Kruger03} adapted the concept to use fragment shaders on a
volume’s bounding box.  Instead of casting rays through a pixel grid, each
fragment generated by rendering the bounding boxes creates its own ray.  The
rays start at the viewpoint and pass through the fragment’s location.  Any
volumes that intersect the ray are sampled at regular intervals along it by
applying the inverse model view matrix to the points and using them as indices
into the volume.  A transfer function converts the values to colors, and each is
blended into the framebuffer at the fragment’s position.  Figure
\ref{fragment-ray-casting} gives a depiction of the process, with green and red
circles representing fragments.

@@

@@

The XML in listing \ref{listing:xml-of-second-pass} shows how the second pass of
the first approach is rendered.  Notice that the render graph supports basic
instancing through the {\em group} and {\em instance} nodes.  When an instance
node is visited, it simply traverses the group it points to.  Complex behavior
can be achieved with nested groups.

\lstset{language=XML}
\lstset{markfirstintag=true}
\lstset{showstringspaces=false}
\lstset{caption=XML of second pass for first approach.}
\lstset{captionpos=b}
\lstset{label=listing:xml-of-second-pass}
\begin{lstlisting}[frame=single,float]
<cull faces="front" />
<framebuffer>
  <attachment usage="color" link="coords-texture-1" />
  <use program="primary-coords-program">
    <group id="intersection-group">
      <booleanAnd of="cube-1 cube-2" />
    </group>
  </use>
</framebuffer>
<framebuffer>
  <attachment usage="color" link="coords-texture-2" />
  <use program="secondary-coords-program">
    <instance of="intersection-group" />
  </use>
</framebuffer>
<cull faces="back" />
<framebuffer>
  <attachment usage="color" link="results-texture" />
  <use program="second-pass-program">
    <uniform name="CoordsTexture1" link="coords-texture-1" />
    <uniform name="CoordsTexture2" link="coords-texture-2" />
    <uniform name="VolumeTexture1" link="volume-texture-1" />
    <uniform name="VolumeTexture2" link="volume-texture-2" />
    <uniform name="MVPMatrix" usage="modelviewprojection" />
    <instance of="intersection-group" />
  </use>
</framebuffer>
\end{lstlisting}

>>>>

To apply ray-casting to volume rendering with a high-level programmable shading
language, \cite{Kruger03} adapted the concept to use fragment shaders on a
volume’s bounding box.  Instead of casting rays through a pixel grid, each
fragment generated by rendering the bounding boxes creates its own ray.  The
rays start at the viewpoint and pass through the fragment’s location.  Any
volumes that intersect the ray are sampled at regular intervals along it by
applying the inverse model view matrix to the points and using them as indices
into the volume.  A transfer function converts the values to colors, and each is
blended into the framebuffer at the fragment’s position.  Figure
\ref{fragment-ray-casting} gives a depiction of the process, with green and red
circles representing fragments.  Figures \ref{fig:first-pass-of-kruger-method}
and \ref{fig:second-pass-of-kruger-method} show the first and second passes of
the Kruger method.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{back-faces.png}
\caption{First pass of Kruger method.}
\label{fig:first-pass-of-kruger-method}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{kruger.png}
\caption{Second pass of Kruger method.}
\label{fig:second-pass-of-kruger-method}
\end{figure}

@@

The XML in listing \ref{listing:xml-of-second-pass} shows how the second pass
for the depth-masking approach is rendered.  Notice that the render graph
supports basic instancing through the {\em group} and {\em instance} nodes.
When an instance node is visited, it simply traverses the group it points to.
Complex behavior can be achieved with nested groups.

\lstset{language=XML}
\lstset{markfirstintag=true}
\lstset{showstringspaces=false}
\lstset{caption=XML of second pass for depth-masking approach.}
\lstset{captionpos=b}
\lstset{label=listing:xml-of-second-pass}
\begin{lstlisting}[frame=single,float]
<cull faces="front" />
<framebuffer>
  <attachment usage="color" link="coords-texture-1" />
  <use program="primary-coords-program">
    <group id="intersection-group">
      <booleanAnd of="cube-1 cube-2" />
    </group>
  </use>
</framebuffer>
<framebuffer>
  <attachment usage="color" link="coords-texture-2" />
  <use program="secondary-coords-program">
    <instance of="intersection-group" />
  </use>
</framebuffer>
<cull faces="back" />
<framebuffer>
  <attachment usage="color" link="results-texture" />
  <use program="second-pass-program">
    <uniform name="CoordsTexture1" link="coords-texture-1" />
    <uniform name="CoordsTexture2" link="coords-texture-2" />
    <uniform name="VolumeTexture1" link="volume-texture-1" />
    <uniform name="VolumeTexture2" link="volume-texture-2" />
    <uniform name="MVPMatrix" usage="modelviewprojection" />
    <instance of="intersection-group" />
  </use>
</framebuffer>
\end{lstlisting}
